---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fable.timegpt

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/fable.timegpt)](https://CRAN.R-project.org/package=fable.timegpt)
<!-- badges: end -->

The fable.timegpt package provides a fable compatible SDK for the [Nixtla](https://www.nixtla.io/)'s [TimeGPT API](https://docs.nixtla.io/).

## Installation

You can install the development version of fable.timegpt from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mitchelloharawild/fable.timegpt")
```

Using the TimeGPT API requires a token, you can request one at <https://dashboard.nixtla.io/>. It is recommended that you store the token as an R environment variable, which can be done by adding the line `TIMEGPT_TOKEN=<your_token_here>` to the `.Renviron` file (which can be opened with `usethis::edit_r_environ()`). Alternatively you can specify the token directly in the `forecast()` function.

## Example

```{r example}
library(fable.timegpt)
uad <- as_tsibble(USAccDeaths)
fit <- uad |> 
  model(TimeGPT(value))
fit
uad |> 
  autoplot(value) + 
  autolayer(fitted(fit), .fitted, colour = "steelblue", linetype = "dashed")
fc <- fit |> 
  forecast(h = 10, level = c(50, 80, 95))
fc
fc |> 
  autoplot(uad, level = c(50, 80, 95))
```

